What can Issues on GitHub and Google Code tell us about Bug Hazards in Android and Java?

### 2015-02-13 android-stacks.tex
changes introduction

   \item  Cross-type exception wrappings, such as an OutOfMemoryError wrapped in a checked exception.
Trying to handle an instance of OutOfMemoryError ``hidden" in  a checked exception may bring the program
 to an unpredictable state. Such wrappings suggest that, when not adequately used, the Java's hybrid exception
 model may become fault-prone.

@@

 The high prevalence of NullPointerExceptions is aligned with the findings of other research works ~\cite{kim2013predicting,fraser20131600,csallner2004jcrasher} as well as the undocumented runtime 
exceptions signaled by the Android Platform ~\cite{kechagia2014}. If on the one hand, the findings our
 study emphasize the impact of these bug harzards on the application robustness 
by mining a different source of information: the issues created by developers on GitHub and Google Code. On the other hand, 
our work points to bug hazards that were not detected by previous works (i.e., cross-type wrappings, undocumented checked exceptions and 
undocumented runtime exceptions thrown by third-party libraries) which can also negatively affect the application robustness.

>>>>

   \item  Cross-type exception wrappings, such as an OutOfMemoryError wrapped in a checked exception.
Trying to handle an instance of OutOfMemoryError ``hidden" in  a checked exception may bring the program
 to an unpredictable state. Such wrappings suggest that, when not adequately used, the Java's hybrid exception
 model may negatively impact the application robustness.

@@

 The high prevalence of NullPointerExceptions is aligned with the findings of other research works ~\cite{kim2013predicting,fraser20131600,csallner2004jcrasher} as well as the undocumented runtime 
exceptions signaled by the Android Platform ~\cite{kechagia2014}. On the one hand, the findings our
 study emphasize the impact of these bug harzards on the application robustness 
by mining a different source of information as the ones used in previous works. The present work 
mined issues created by developers on GitHub and Google Code, while other works analyzed crash and automated test reports.
 On the other hand, our work points to bug hazards that were not detected by previous works (i.e., cross-type wrappings, undocumented checked exceptions and undocumented runtime exceptions thrown by third-party libraries) which can also negatively affect the application robustness.
